---
title: "Public Art Mapping in Portland"
author: "Winston Saunders"
date: "May 31, 2015"
output: html_document
---

To get the data use the following function. The data are stored in my GitHub.

```{r "get data", echo=9:13}        
        ## define a read_data function which will be used to pull data from my gitbhub acct
        ## 
        library(RCurl)
        readData <- function(path.name, file.name, column.types, missing.types) {
                ## create URL from path and file names
                myData<-getURL(paste0(path.name, file.name) )
                ## read the data
                read.csv(textConnection(myData),
                colClasses=column.types,
                na.strings=missing.types )
                
            }

```

The variables for the function are defined as below. 
The train.column.types simplifies the data cleaning for the analysis.

```{r, echo=FALSE, warning=FALSE}

        file.path <- "https://raw.githubusercontent.com/ww44ss/public_art/master/"
        data.file <- "public_art.csv"
        missing.types <- c("NA", "")

        train.column.types <- c('integer',   # record_id
                                'character',    # artist 
                                'character',    # title
                                'character',         # date
                                'factor',       # medium
                                'factor',       # discipline
                                'character',    # dimensions
                                'charcter',     # funding_source
                                'character',    # location
                                'character',    # street
                                'character',    # city
                                'factor',       # zipcode
                                "numeric",      # latitude
                                "numeric",      # longitude
                                "character",    # description
                                "character",    # image URL
                                "character",    # detail URL
                                "character"     # date_modified
        )

        test.column.types <- train.column.types[-2]     # # no Survived column in test.csv
```


Now we can get the data quickly

```{r, echo=3:7}
        setwd("/Users/winstonsaunders/Documents/TitanicKaggle")
        ##Okay let's get the data
        training <- readData(Titanic.path, train.data.file, train.column.types, missing.types)
        testing <-  readData(Titanic.path, test.data.file, test.column.types, missing.types)

        trainingRaw<-training
        testingRaw<-testing

```

```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
